\addcontentsline{toc}{chapter}{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}

\renewcommand\bibname{СПИСОК ИСПОЛЬЗОВАННЫХ ИСТОЧНИКОВ}
\begin{thebibliography}{}
	
\setlength\bibindent{1.25cm}
\makeatletter
\let\old@biblabel\@biblabel
\def\@biblabel#1{\kern\bibindent\old@biblabel{#1}}
\makeatother

\bibitem{stats} Linux Statistics 2024 [Электронный ресурс]. --- URL: \url{https://truelist.co/blog/linux-statistics/} (дата обращения: 01.02.2024).

\bibitem{net} Benvenuti C. Understanding Linux Network Internals, 2005. 1062 p.

\bibitem{guide} Illustrated Guide to Monitoring and Tuning the Linux Networking Stack: Receiving Data [Электронный ресурс]. --- URL: \url{https://blog.packagecloud.io/illustrated-guide-monitoring-tuning-linux-networking-stack\\-receiving-data/} (дата обращения: 07.01.2024).

\bibitem{softnet_data} softnet\_data identifier -- Linux source code (v6.7) [Электронный ресурс]. --- URL: \url{https://elixir.bootlin.com/linux/v6.7/source/include/linux/netdevice.h#L3238} (дата обращения: 07.01.2024).

\bibitem{rec} Monitoring and Tuning the Linux Networking Stack: Receiving Data [Электронный ресурс]. --- URL: \url{https://blog.packagecloud.io/monitoring-tuning-linux-networking-stack-receiving-data/} (дата обращения: 07.01.2024).

\bibitem{napi_schedule} \_\_\_\_napi\_schedule identifier -- Linux source code (v6.7) [Электронный ресурс]. --- URL: \url{https://elixir.bootlin.com/linux/v6.7/source/net/core/dev.c#L4437} (дата обращения: 07.01.2024).

\bibitem{napi_struct} napi\_struct identifier -- Linux source code (v6.7) [Электронный ресурс]. --- URL: \url{https://elixir.bootlin.com/linux/v6.7/source/include/linux/netdevice.h#L354} (дата обращения: 07.01.2024).

\bibitem{net_rx_action} net\_rx\_action identifier -- Linux source code (v6.7) [Электронный ресурс]. --- URL: \url{https://elixir.bootlin.com/linux/v6.7/source/net/core/dev.c#L6701} (дата обращения: 07.01.2024).

\bibitem{send} Monitoring and Tuning the Linux Networking Stack: Sending Dataa [Электронный ресурс]. --- URL: \url{https://blog.packagecloud.io/monitoring-tuning-linux-networking-stack-sending-data/} (дата обращения: 07.01.2024).

\bibitem{qdisc_run} \_\_qdisc\_run identifier -- Linux source code (v6.7) [Электронный ресурс]. --- URL: \url{https://elixir.bootlin.com/linux/v6.7/source/net/sched/sch_generic.c#L410} (дата обращения: 07.01.2024).

\bibitem{netif_reschedule} \_\_netif\_reschedule identifier -- Linux source code (v6.7) [Электронный ресурс]. --- URL: \url{https://elixir.bootlin.com/linux/v6.7/source/net/core/dev.c#L3087} (дата обращения: 07.01.2024).

\bibitem{net_tx_action} net\_tx\_action identifier -- Linux source code (v6.7) [Электронный ресурс]. --- URL: \url{https://elixir.bootlin.com/linux/v6.7/source/net/core/dev.c#L5123} (дата обращения: 07.01.2024).

\end{thebibliography}